---
title: "Homework 1"
author: "Suraj Bodhanandan Nhattuvetty - 23200338"
format: 
  pdf: 
    geometry:
      - top=30mm
      - left=20mm
      - heightrounded
    colorlinks: true
editor: visual
---

# Introduction

The dataset being examined is the built-in dataset **mtcars**. The dataset contains variables which are based on the design and performance of different cars.

```{r}
#| label: head-mtcars
#| echo: false
#Overview of dataset
head(mtcars)
```

# Analysis

Below a quick summary of the variables and a plot to check the relationship between two variables can be found

## Summary of Variables

The following values are found when we summarise the variables in the **mtcars** dataset:

-   Minimum

-   1^st^ Quantile

-   Median

-   Mean

-   3^rd^ Quantile

-   Maximum

{{< pagebreak >}}

```{r}
#| label: summary-mtcars
#| echo: false
#Summarise the mtcars dataset
summary(mtcars)
```

There are 11 variables in the dataset and all of them are numerical variables.

## Plot

We can plot the variables **mpg** and **hp** to check what kind of relation they have.

```{r}
#| label: plot-mtcars
#| echo: false
#Scatter plot of mpg vs hp
plot(mtcars$mpg, mtcars$hp, main = 'MPG vs HP', col = 'blue',
     xlab = 'Miles per gallon', ylab = 'Horsepower')
```

From the plot, it can be seen that there is a negative relationship between **mpg** and **hp**. As horsepower increases the miles per gallon for the car decreases.
